A Large-Scale Study of the Use of Eval in R

### 2020-08-26 inst/paper/main.tex
P
Add basic infrastructure details

This section describes the infrastructure we used to run the dynamic program
analysis to record the calls to evals.

@@

We endeavored  to write these functions without \eval. \c{match.arg} appears in 60.1\% of the eval calls. It is used to get the arguments, possibly abbreviated, of a function. With one argument, as \c{match.arg(arg)}, it uses \c{eval} to infer them from a parent function's formal arguments. We can rewrite it using its version with two arguments, \c{match.arg(arg, choices)} where \c{choices} are the possible formal arguments of the function, as shown in Listing~\ref{code:matcharg}.

>>>>

This section describes the infrastructure we used to run the dynamic program
analysis to record the calls to evals. Our analysis pipeline starts with
downloading and installing the open source R packages from CRAN. The Kaggle
kernels are downloaded from Kaggle.com by a crawler and handled separately.
Next, we extract code size and coverage metrics from the installed packages
using the covr package.
This is followed by extraction of runnable programs from R packages: tests,
examples and vignettes. The extracted programs are then executed through our
dynamic analyzer, instrumentr, which obtains relevant information from the
program runs. instrumentr is an R package that enables us to write our tracing
logic in R. It internally uses R-dyntrace which is a modified R interpreter that
exposes hooks for events of interest. instrumentr provides an API to execute R
callbacks from these hooks.
Finally, we use RMarkdown notebooks to analyze and visualize this data.
Our infrastructure contains three
components:
Figure~\ref{fig:pipeline} shows the main steps of our pipeline.

@@

We endeavored  to write these functions without \eval. \c{match.arg} appears in \MatchArgPercent of the \eval calls. It is used to get the arguments, possibly abbreviated, of a function. With one argument, as \c{match.arg(arg)}, it uses \c{eval} to infer them from a parent function's formal arguments. We can rewrite it using its version with two arguments, \c{match.arg(arg, choices)} where \c{choices} are the possible formal arguments of the function, as shown in Listing~\ref{code:matcharg}.
